---
title: "Introduction to binomial"
author: "Mark Nevins"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
library(binomial)
```

## Binomial Distribution
The package `"binomial"` is a basic package that calculates the probabilities and various statistics about a binomial distribution with
the given parameters after checking that the parameters are valid, and displays both the distribution and cumulative distribution of
the chosen binomial distribution.

## Combination function

The most basic thing in this package is a rudimentary combination function, `bin_choose(n,k)`, which calculates n choose k if the inputs are valid.

```{r}
bin_choose(5,2)
```

## Create a binomial variable

The most straightforward thing we can do is create an object of type `"binvar"` that holds the number of trials and probability of our
Binomial Distribution using `bin_variable(trials, prob)`:

```{r}
binomial <- bin_variable(5,0.5)
binomial
```

`bin_variable()` is by default set to 1 trial with probability 1.

## Find the summary measures

With this `"binvar"` object, we can easily see important statistical calculations of the distribution by invoking the method `summary()` on it.

```{r}
summary(binomial)
```

We can also find each specific measure with `"bin_"` + `"measure"`, but the trial and probability must be inputted manually.

```{r}
bin_mean(5,0.5)
bin_variance(5,0.5)
bin_mode(5,0.5)
bin_skewness(5,0.5)
bin_kurtosis(5,0.5)
```


## Find a specific probability

Using `bin_probability(success, trials, prob)`, we can calculate the probability of a certain amount of successes given the amount of trials and the probability of success. The success variable can be a vector.

```{r}
bin_probability(2,5,0.5)
bin_probability(0:2,5,0.5)
```

## Plot distributions

Using `bin_distribution(trials, prob)` in combination with `plot()` allows us to plot the distribution.

```{r}
plotdist <- bin_distribution(5,0.5)
plot(plotdist)
```

The cumulative distribution can also be plotted, this time using `bin_cumulative(trials, prob)` in conjunction with `plot()`.

```{r}
plotcum <- bin_cumulative(5,0.5)
plot(plotcum)
```
